### 2021-05-12 proposal/proposal.tex
updated proposal

%\begin{titlepage}
\begin{center}
\LARGE{\textbf{Community Detection Methods for Random Dot Product Graphs and Generalized Random Dot Product Graphs}}\\
\vspace*{2\baselineskip}
\normalsize{A dissertation proposal submitted in partial satisfaction of the requirements for the degree of \\}
Doctor of Philosophy \\
in \\
Statistical Science \\
\vspace*{2\baselineskip}
\Large{John Koo}\\
\vspace*{3\baselineskip}
\Large{\textbf{Research Committee Members}}\\
Dr. Michael Trosset \\
Dr. Minh Tang \\
Dr. Julia Fukuyama \\
Dr. Roni Khardon \\
Dr. Fangzheng Xie \\
\vspace*{3\baselineskip}
Date TBA \\
\vspace*{1\baselineskip}
Department of Statistics \\
Indiana University \\
Bloomington, Indiana \\
\end{center}
% \end{titlepage}

@@

Graph and network data have become increasingly widespread in various
fields including sociology, neuroscience, biostatistics, and computer
science. This has resulted in various challenges for researchers who
rely on traditional statistical and machine learning methods, many of
which are incompatible with graph data and instead require the data to
exist as feature vectors in Euclidean space. Such challenges often
involve clustering and community detection. Common clustering methods
typically involve calculating some central or representative point for
each cluster around which the data belonging to that cluster lie (e.g.,
Lloyd's algorithm for \(K\)-means clustering \cite{1056489}, Gaussian
Mixture Models \cite{doi:10.1198/016214502760047131}). Because these
methods involve computing summary statistics within each cluster, such
as the sample average, they cannot be applied directly to graphs,
necessitating methods for transforming the graph data into feature
vectors.

@@

Let \(G = (V, E)\) be an undirected, unweighted graph with no self-loops
with \(n\) vertices. Denote \(A \in \{0, 1\}^{n \times n}\) as the
adjacency matrix for \(G\) such that \(A_{ij} = 1\) if there exists an
edge between vertices \(i\) and \(j\) and \(A_{ij} = 0\) otherwise.
Because \(G\) is symmetric and contains no self-loops,
\(A_{ij} = A_{ji}\) and \(A_{ii} = 0\) for \(i, j \in [n]\). We further
restrict our analyses to independent Bernoulli graphs. Let
\(P \in [0, 1]^{n \times n}\) be a symmetric matrix of edge
probabilities. Graph \(G\) is sampled from \(P\) by drawing
\(A_{ij} \stackrel{\text{indep}}{\sim}\text{Bernoulli}(P_{ij})\) for
each \(0 \leq i < j \leq n\) (\(A_{ji} = A_{ij}\) and \(A_{ii} = 0\)).
Finally, we denote
\(X = \begin{bmatrix} x_1 & \cdots & x_n \end{bmatrix}^\top \in \mathbb{R}^{n \times d}\)
as the sample \(x_1, ..., x_n \in \mathbb{R}^d\), and denote
\(z_1, ..., z_n \in [K]\) as their corresponding (hidden) labels.

@@

Generative models for symmetric Bernoulli graphs involve defining the
edge probability matrix \(P\) whose \(ij\)\textsuperscript{th} entry is
the probability of an edge between vertices \(i\) and \(j\) for each
\(i, j \in [n]\). In order to motivate community detection methods, we
restrict the generative model such that for each pair of vertices, the
probability of an edge between the vertices is conditioned on the labels
of the vertices. One such model is the Stochastic Block Model (SBM)
\cite{doi:10.1080/0022250X.1971.9989788}: Given \(K\) communities and
each vertex belonging to one community, the SBM restricts \(P\) to
\(K (K + 1) / 2\) unique entries such that \(P_{ij} = B_{z_i z_j}\) and
\(B \in [0, 1]^{K \times K}\) with entries \(B_{kl}\) denoting the edge
probability of each vertex in community \(k\) having an edge with each
vertex in community \(l\). The homogeneous SBM further restricts \(P\)
to two unique entries such that \(P_{ij} = p\) if \(z_i = z_j\) and
\(P_{ij} = q\) otherwise. Multiple generalizations of the SBM have been
introduced since, including the Degree Corrected Block Model (DCBM) and
the Popularity Adjusted Block Model (PABM). Like the SBM, these models
involve edge probability matrix \(P\) that is restricted to rank
\(d < n\) in part based on community labels.

@@

It is straightforward to show that all Bernoulli graphs with positive
semidefinite \(P\) are special cases of the RDPG, which is a special
case of the GRDPG, and all graphs generated by \(P\) are special cases
of the GRDPG. This includes the SBM, DCBM, and PABM. In the following
example, we show that the ASE of the SBM has a very particular form.

\begin{example}[Connecting the SBM to the RDPG]
Let $G = (V, E)$ with adjacency matrix $A$ be sampled from the homogeneous SBM with two communities such that within-community edge probability $p$ and between-community edge probability $q$ where $p > q$. Let community 1 have $n_1$ vertices and community 2 have $n_2$ vertices such that $n_1 + n_2 = n$. Without loss of generality, organize $P$ and $A$ such that the $kl^{th}$ block represents edges between communities $k$ and $l$. Then $P = \begin{bmatrix} P^{(11)} & P^{(12)} \\ P^{(21)} & P^{(22)} \end{bmatrix}$ where each block is a constant value, e.g., $P^{(11)}_{ij} = p$. One RDPG representation of this SBM is:

@@

Given sufficiently large sample size \(n\), the scaled ASE of affinity
matrix \(A\) drawn from a RDPG or GRDPG will asymptotically approach the
original latent positions \(X\) with probability 1, up to a linear
transformation (orthogonal transformation for the RDPG, a composition of
an orthogonal and scale transformations for the GRDPG). Thus if \(X\)
consists of points that lie on subspaces of \(\mathbb{R}^d\), then both
the scaled and unscaled ASE of \(A \sim \text{RDPG}(X)\) or
\(A \sim \text{GRDPG}(X)\) will consist of points that lie near
subspaces, with some noise that almost surely goes to \(0\) as
\(n \to \infty\), motivating ASE followed by SSC as an asymptotically
consistent method for community detection. The Popularity Adjusted Block
Model (PABM) \cite{307cbeb9b1be48299388437423d94bf1} is a generative
graph model with underlying communities such that each community lies on
a subspace. \citet{noroozi2019estimation} showed that SSC is able to
recover the subspaces and therefore perform community detection for the
PABM given \(P = X I_{p, q} X^\top\), the edge probability matrix,
rather than \(A\), the adjacency matrix. Combining the results of
\citeauthor{rubindelanchy2017statistical} and
\citeauthor{jmlr-v28-wang13}, it should be possible to recover the
communities using \(A\) as well.

@@

\citet{trosset2020learning} showed that the ASE of a RDPG can be used to
recover one-dimensional manifolds. Suppose
\(f : [0, 1] \mapsto \mathcal{X}\) such that \(f\) is smooth and
\(\mathcal{X}\) represents a curve or one-dimensional manifold in
\(\mathbb{R}^d\). If \(t_1, ..., t_n \stackrel{iid}{\sim} F\) such that
\(F\) has support \([0, 1]\), the latent positions are \(x_i = f(t_i)\)
with \(y_i\) is its corresponding point in the scaled ASE, and
\(d_{\epsilon}(\cdot, \cdot)\) is the shortest path distance of an
\(\epsilon\)-neighborhood graph. Under certain mild conditions, the
shortest path distances of the \(\epsilon\)-neighborhood graph of the
ASE approaches the arc lengths along \(f\):

@@

It is trivial to show that the PABM, as well as all graphs such that the
adjacency matrix is drawn such that \(A_{ij} \sim Bernoulli(P_{ij})\),
is a special case of the GRDPG. It can also be shown that the latent
positions of the PABM under the GRDPG framework consists of \(K\)
\(K\)-dimensional subspaces in \(\mathbb{R}^{K^2}\). While there is no
unique latent configuration \(X\) such that \(X X^\top = P\), the edge
probability \(P\) for the PABM, they all have this subspace structure,
and one in particular consists of \emph{orthogonal} subspaces.

@@

In Theorem \ref{theorem2}, we showed that a possible latent
configuration for a \(K\)-community PABM under the GRDPG framework
consists of latent positions in \(\mathbb{R}^{K^2}\) such that each
community corresponds to a \(K\)-dimensional subspace such that each
subspace is orthogonal to the others.

@@

If \(\hat{V}\) is the \emph{unscaled} ASE of \(A\), then results from
\citeauthor{rubindelanchy2017statistical} imply
\(n \hat{V} \hat{V}^\top \stackrel{a.s.}{\to} n V V^\top\). Then for
vertices \(i\) and \(j\) belonging to separate communities, the
\(ij\)\textsuperscript{th} entry of \(n \hat{V} \hat{V}^\top\)
approaches 0 with probability 1:

@@

In addition to OSC, since the communities are subspaces in the latent
space, we can leverage existing methods for subspace clustering. Of
particular interest is Sparse Subspace Clustering (SSC), which is
performed by solving an optimization problem for each observed point in
a sample. Given \(X \in \mathbb{R}^{n \times d}\) with vectors
\(x_i^\top \in \mathbb{R}^d\) as rows of \(X\), the optimization problem
\(c_i = \min\limits_{c} \|c\|_1\) subject to \(x_i = X_{-i} c\) and
\(c^{(i)} = 0\) is solved for each \(i \in [n]\). The solutions are
collected into matrix
\(C = \begin{bmatrix} c_1 & \cdots & c_n \end{bmatrix}^\top\) to
construct affinity matrix \(B = |C| + |C^\top|\). If each \(x_i\) lie
perfectly on one of \(K\) subspaces, \(B\) is sparse such that
\(B_{ij} = 0\) \(\forall x_i, x_j\) belonging to different subspaces.
Then \(B\) can describe a graph with at least \(K\) disjoint subgraphs,
and if the number of subgraphs is exactly \(K\), each subgraph maps onto
a subspace.

@@

\begin{remark} 
In practice, a noisy sample $X$ often does not obey SDP. 
In such cases, $B$ is treated as an affinity matrix for a graph which 
is then partitioned into $K$ subgraphs to obtain the clustering. On the other 
hand, if $X$ does obey the SDP, $B$ describes a graph 
with at least $K$ disconnected subgraphs. Ideally, when SDP holds, 
there are exactly $K$ subgraphs which map to each subspace, 
but it could be the case that some of the subspaces are represented by 
multiple disconnected subgraphs. SDP is contingent 
on choosing a sufficiently large sparsity parameter $\lambda$. 
\end{remark}

Since every ASE of the PABM consists of subspaces and as
\(n \to \infty\) each point of the ASE approaches its subspace almost
surely, SSC should also work for PABM community detection. Combining
this with the results by \citeauthor{jmlr-v28-wang13}, which state that
if the points lie sufficiently close to their respective subspaces and
the cosine of the angles between subspaces is sufficiently small, SDP
will hold. We show that the unscaled ASE exhibits exactly these
conditions for sufficiently large \(n\).

\begin{theorem}
\label{theorem5}
Let $P_n$ describe the edge probability matrix of the PABM with 
$n$ vertices, and let $A_n \sim \text{Bernoulli}(P_n)$.  Let $\hat{V}_n$ be the 
matrix of eigenvectors of $A_n$ corresponding to the $K (K + 1) / 2$ most
positive and $K (K - 1) / 2$ most negative eigenvalues. Then 
$\exists \lambda > 0$ and $N \in \mathbb{N}$ such that when $n > N$, 
$\sqrt{n} \hat{V}_n$ obeys the subspace detection property with probability 1.
\end{theorem}

@@

In the previous sections, we connected well-known and highly structured
generative graph models to the RDPG and GRDPG to show that highly
structured latent configurations generate graphs consistent with these
models: The latent space for the SBM consists of \(K\) point masses, the
latent space for the DCBM consists of \(K\) rays emanating from the
origin, and the latent space for the PABM consists of \(K\)
\(K\)-dimensional subspaces. In the following sections, we explore
additional structured latent configurations corresponding to community
structure and develop methods for community detection based on the
consistency of the ASE and the structural forms of the latent
configurations.

@@

@@

If we extend this example such that \(n_1\) points are sampled uniformly
from the segment \(f_1(t) = (t, 0)\) and \(n_2\) points are sampled
uniformly from the segment \(f_2(t) = (t, a)\) for \(t \in [0, 1]\),
then a sample of size \(N(\delta, a)\) is sufficient to satisfy:

>>>>

%\begin{titlepage}
\begin{center}
\LARGE{\textbf{Community Detection Methods for the Generalized Random Dot Product Graph Model}}\\
\vspace*{2\baselineskip}
\normalsize{A dissertation proposal submitted in partial satisfaction of the requirements for the degree of \\}
Doctor of Philosophy \\
in \\
Statistical Science \\
\vspace*{2\baselineskip}
\Large{John Koo}\\
\vspace*{3\baselineskip}
\Large{\textbf{Research Committee Members}}\\
Dr. Michael Trosset \\
Dr. Minh Tang \\
Dr. Julia Fukuyama \\
Dr. Roni Khardon \\
Dr. Fangzheng Xie \\
\vspace*{3\baselineskip}
Date TBA \\
\vspace*{1\baselineskip}
Department of Statistics \\
Indiana University \\
Bloomington, Indiana \\
\end{center}
% \end{titlepage}

@@

Graph and network data have become increasingly widespread in various
fields including sociology, neuroscience, biostatistics, and computer
science. This has resulted in various challenges for researchers who
rely on traditional statistical and machine learning methods, many of
which are incompatible with graph data and instead require the data to
exist as feature vectors in Euclidean space. Such challenges often
involve clustering and community detection, which are often the goal of
graph data analysis. Common clustering methods typically involve
calculating some central or representative point for each cluster around
which the data belonging to that cluster lie (e.g., Lloyd's algorithm
for \(K\)-means clustering \cite{1056489}, Gaussian Mixture Models
\cite{doi:10.1198/016214502760047131}). Because these methods involve
computing summary statistics within each cluster, such as the sample
average, they cannot be applied directly to graphs, necessitating
methods for transforming the graph data into feature vectors.

@@

Let \(G = (V, E)\) be an undirected, unweighted graph with no self-loops
and \(n\) vertices. Denote \(A \in \{0, 1\}^{n \times n}\) as the
adjacency matrix for \(G\) such that \(A_{ij} = 1\) if there exists an
edge between vertices \(i\) and \(j\) and \(A_{ij} = 0\) otherwise.
Because \(G\) is symmetric and contains no self-loops,
\(A_{ij} = A_{ji}\) and \(A_{ii} = 0\) for \(i, j \in [n]\). We further
restrict our analyses to independent Bernoulli graphs. Let
\(P \in [0, 1]^{n \times n}\) be a symmetric matrix of edge
probabilities. Graph \(G\) is sampled from \(P\) by drawing
\(A_{ij} \stackrel{\text{indep}}{\sim}\text{Bernoulli}(P_{ij})\) for
each \(1 \leq i < j \leq n\) (\(A_{ji} = A_{ij}\) and \(A_{ii} = 0\)).
Finally, we denote
\(X = \begin{bmatrix} x_1 & \cdots & x_n \end{bmatrix}^\top \in \mathbb{R}^{n \times d}\)
as the sample \(x_1, ..., x_n \in \mathbb{R}^d\) and
\(z_1, ..., z_n \in [K]\) as their corresponding (hidden) labels.

@@

Generative models for independent Bernoulli graphs involve defining the
edge probability matrix \(P\) whose \(ij\)\textsuperscript{th} entry is
the probability of an edge between vertices \(i\) and \(j\) for each
\(i, j \in [n]\). In order to motivate community detection methods, we
restrict the generative model such that for each pair of vertices, the
probability of an edge between the vertices is conditioned on their
labels. One such model is the Stochastic Block Model (SBM)
\cite{doi:10.1080/0022250X.1971.9989788}: Given \(K\) communities and
each vertex belonging to one community, the SBM restricts \(P\) to
\(K (K + 1) / 2\) unique entries such that \(P_{ij} = p_{z_i z_j}\)
where \(p_{kl} = p_{lk}\) is the probability of an edge between each
vertex in community \(k\) to each vertex in community \(l\). The
homogeneous SBM further restricts \(P\) to two unique entries:
\(P_{ij} = p\) if \(z_i = z_j\) and \(P_{ij} = q\) otherwise. Several
generalizations of the SBM have been introduced since, including the
Degree Corrected Block Model (DCBM) and the Popularity Adjusted Block
Model (PABM). Like the SBM, these models involve imposing some
restriction on \(P\) based on community labels (and possibly other
factors).

@@

It is straightforward to show that all Bernoulli graphs with positive
semidefinite \(P\) are special cases of the RDPG, which is a special
case of the GRDPG, and all graphs generated by \(P\) are special cases
of the GRDPG. This includes the SBM, DCBM, and PABM. In the following
example, we show that under the RDPG framework, the latent configuration
that induces the SBM takes on a very particular form.

\begin{example}[Connecting the SBM to the RDPG]
Let $G = (V, E)$ with adjacency matrix $A$ be sampled from the SBM with two communities for which the within-edge probabilities are $p$ and $q$ for communities 1 and 2 respective, and the between-community edge probability is $r$, with $p q > r^2$. Let community 1 have $n_1$ vertices and community 2 have $n_2$ vertices such that $n_1 + n_2 = n$. Without loss of generality, organize $P$ and $A$ such that the $kl^{th}$ block represents edges between communities $k$ and $l$. Then $P = \begin{bmatrix} P^{(11)} & P^{(12)} \\ P^{(21)} & P^{(22)} \end{bmatrix}$ where each block is a constant value, e.g., $P^{(11)}_{ij} = p$. One RDPG representation of this SBM is:

@@

@@

\citet{trosset2020learning} showed that the ASE of a RDPG can be used to
recover one-dimensional manifolds. Suppose
\(f : [0, 1] \mapsto \mathcal{X}\) such that \(f\) is smooth and
\(\mathcal{X}\) represents a curve or one-dimensional manifold in
\(\mathbb{R}^d\). If \(t_1, ..., t_n \stackrel{\text{iid}}{\sim}F\) such
that \(F\) has support \([0, 1]\), the latent positions are
\(x_i = f(t_i)\) with \(y_i\) is its corresponding point in the scaled
ASE, and \(d_{\epsilon}(\cdot, \cdot)\) is the shortest path distance of
an \(\epsilon\)-neighborhood graph. Under certain mild conditions, the
shortest path distances of the \(\epsilon\)-neighborhood graph of the
ASE approaches the arc lengths along \(f\):

@@

It is straightforward to show that the PABM, as well as all graphs such
that the adjacency matrix is drawn such that
\(A_{ij} \stackrel{\text{indep}}{\sim}Bernoulli(P_{ij})\), is a special
case of the GRDPG. It can also be shown that the latent positions of the
PABM under the GRDPG framework consists of \(K\) \(K\)-dimensional
subspaces in \(\mathbb{R}^{K^2}\). While there is no unique latent
configuration \(X\) such that \(X X^\top = P\), the edge probability
\(P\) for the PABM, they all have this subspace structure, and one in
particular consists of \emph{orthogonal} subspaces.

@@

In Theorem \ref{theorem2}, we showed that a possible latent
configuration for a \(K\)-community PABM under the GRDPG framework
consists of vectors in \(\mathbb{R}^{K^2}\) such that each community
corresponds to a \(K\)-dimensional subspace and each subspace is
orthogonal to the others.

@@

If \(\hat{V}\) is the \emph{unscaled} ASE of \(A\), then results from
\citet{rubindelanchy2017statistical} imply
\(n \hat{V} \hat{V}^\top \stackrel{a.s.}{\to} n V V^\top\). Then for
vertices \(i\) and \(j\) belonging to separate communities, the
\(ij\)\textsuperscript{th} entry of \(n \hat{V} \hat{V}^\top\)
approaches 0 with probability 1:

@@

Since the communities are subspaces in the latent space, we can also use
existing methods for subspace clustering on the ASE. Of particular
interest is Sparse Subspace Clustering (SSC), which is performed by
solving an optimization problem for each observed point in a sample.
Given \(X \in \mathbb{R}^{n \times d}\) with vectors
\(x_i^\top \in \mathbb{R}^d\) as rows of \(X\), the optimization problem
\(c_i = \min\limits_{c} \|c\|_1\) subject to \(x_i = X_{-i} c\) and
\(c^{(i)} = 0\) is solved for each \(i \in [n]\). The solutions are
collected into matrix
\(C = \begin{bmatrix} c_1 & \cdots & c_n \end{bmatrix}^\top\) to
construct affinity matrix \(B = |C| + |C^\top|\). If each \(x_i\) lie
perfectly on one of \(K\) subspaces, \(B\) is sparse such that
\(B_{ij} = 0\) \(\forall x_i, x_j\) belonging to different subspaces.
Then \(B\) can describe a graph with at least \(K\) disjoint subgraphs,
and if the number of subgraphs is exactly \(K\), each subgraph maps onto
a subspace.

@@

\begin{remark} 
In practice, a noisy sample $X$ often does not obey SDP. 
In such cases, $B$ is treated as an affinity matrix for a graph which 
is then partitioned into $K$ subgraphs to obtain the clustering. On the other 
hand, if $X$ does obey the SDP, $B$ describes a graph 
with at least $K$ disconnected subgraphs. Ideally, when SDP holds, 
there are exactly $K$ subgraphs which map to each subspace, 
but it could be the case that some of the subspaces are represented by 
multiple disconnected subgraphs.
\end{remark}

Since every ASE of the PABM consists of subspaces and as
\(n \to \infty\) each vector of the ASE approaches its subspace
uniformly \cite{rubindelanchy2017statistical}, SSC is also able to
perform community detection for the PABM. It has been shown by
\citet{jmlr-v28-wang13} that if the points lie sufficiently close to
their respective subspaces and the cosine of the angles between
subspaces is sufficiently small, SDP will hold. We now state that the
unscaled ASE of the PABM exhibits exactly these conditions for
sufficiently large \(n\).

\begin{theorem}
\label{theorem5}
Let $P_n$ describe the edge probability matrix of the PABM with 
$n$ vertices, and let $A_n \sim \text{Bernoulli}(P_n)$.  Let $\hat{V}_n$ be the 
matrix of eigenvectors of $A_n$ corresponding to the $K (K + 1) / 2$ most
positive and $K (K - 1) / 2$ most negative eigenvalues. Then 
$\exists \lambda > 0$ and $N < \infty$ such that when $n > N$, 
$\sqrt{n} \hat{V}_n$ obeys the subspace detection property with probability 1.
\end{theorem}

\hypertarget{alternative-approaches-to-community-detection}{%
\paragraph{Alternative Approaches to Community
Detection}\label{alternative-approaches-to-community-detection}}

So far, we connected the PABM to the GRDPG and used this to motivate
community detection methods based on the ASE of the adjacency matrix
sampled from the PABM. In this section, we will explore non-spectral
methods for community detection.

Denoting \(\{\lambda_{ik}\}\) as the scalar popularity parameters for
the PABM such that \(\lambda^{(kl)}\) is the vector of \(\lambda_{jl}\)
terms for which vertex \(j\) is in community \(k\), we can write the
likelihood for the PABM:

\[p(A | z, \{\lambda_{ik}\}) = 
\prod_{i < j} (\lambda_{i z_j} \lambda_{j z_i})^{A_{ij}} 
(1 - \lambda_{i z_j} \lambda_{j z_i})^{1 - A_{ij}}\]

\begin{equation}
= \prod_{i < j} \prod_k^K \prod_l^K 
(\lambda_{il} \lambda_{jk})^{A_{ij} z_{ik} z_{jl}} 
(1 - \lambda_{il} \lambda_{jk})^{(1 - A_{ij}) z_{ik} z_{jl}}
\end{equation}

where \(z_{ik} = I(Z_i = k)\).

The log-likelihood is

\begin{equation}
\log p = \sum_{i < j} \sum_k \sum_l z_{ik} z_{jl} 
(A_{ij} \log \lambda_{il} \lambda_{jk} + 
(1 - A_{ij}) \log (1 - \lambda_{il} \lambda_{jk}))
\end{equation}

While direct maximization of the likelihood or log-likelihood is
NP-complete, it is possible to apply an Expectation Maximization (EM)
algorithm to this problem.

@@

In the previous sections, we connected well-known and highly restricted
generative graph models to the RDPG and GRDPG to show that highly
structured latent configurations generate graphs consistent with these
models: The latent space for the SBM consists of \(K\) point masses, the
latent space for the DCBM consists of \(K\) rays emanating from the
origin, and the latent space for the PABM consists of \(K\)
\(K\)-dimensional subspaces. In the following sections, we explore
additional structured latent configurations corresponding to community
structure and develop methods for community detection based on the
consistency of the ASE and the structural forms of the latent
configurations.

@@

\begin{figure}[H]

{\centering \includegraphics{proposal_files/figure-latex/unnamed-chunk-1-1}

}

\caption{Points sampled uniformly on two parallel unit length line segments}\label{fig:unnamed-chunk-1}
\end{figure}

@@

If we extend this example such that \(n_1\) points are sampled uniformly
from the segment \(f_1(t) = (t, 0)\) and \(n_2\) points are sampled
uniformly from the segment \(f_2(t) = (t, a)\) for \(t \in [0, 1]\),
then a sample of size \(\min(n_1, n_2) \geq N(\delta, a)\) is sufficient
to satisfy:
